\chapter{Conclusion}
\label{chap:conclusion}

We are happy with choosing Unity as our engine as we learned a lot of new things in the process of developing the game. We got a better understanding of the HLAPI and its strengths as well as weaknesses. The Unity low level API was also available, but we didn't delve too much into its functionalities. There are currently alternatives to the HLAPI in development~\cite{photonThunder} which could fix some of the issues we experienced and having already used the HLAPI allows us to better judge and compare these API's in the future.

We ended up with a good and flexible architecture in terms of adding new Docking Kits, Abilities and Modifiers as seen from the amount of kits we ended up making. This is also in part thanks to \emph{Scriptable Objects} which we learned to use during development. The knowledge of how to use \emph{Scriptable Objects} is something that will be very useful for any future development in Unity. 

The game might not have gotten as robust networking wise as we might have wanted due to there not being time for much polish, but despite this, we didn't run into any major network related bugs during playtesting so the code and architecture is fairly stable in that regard. We managed to meet our learning goals by implementing a large project with large networked components although there wasn't much time for balancing other than the initial balance iteration. Designing and implementing docking kits with varying and interesting abilities ended up being quite the challenge, but we are very happy with the amount of kits we managed to implement in the end. 

We gained experience with how to use tools like Jira by integrating it with BitBucket and managing issues in the backlog through the use of smart commits. We also found Jira to be a very helpful tool for Scrum activities like planning poker and managing sprints. Confluence was less used than originally intended, but we still attained some further knowledge by using it as a tool for meeting notes and design decision documentation. 

\section{Future Work}
\label{sec:future}
As we mentioned in Section~\ref{sec:feedbackReflect} we will be spending some time before the presentation to polish the game and visuals. We might also end up taking some of the other feedback from the playtesters and tweak various parts of the game while doing the visual polish for a better game experience. Other than that, we have no future plans for the development of the game after the presentation.  
